Approximation as Differentiation

### 2025-07-08 main/approx-as-tangents.tex
Tangent categores, Cartesian differential categories.

We end this section with a conjecture. Although we have argued above
that there is an analogy between stable functions and smooth
functions, we have not stated any mathematical theorems substantiating
this. \emph{Tangent Categories} \cite{tangent-categories} are a
categorical axiomatisation of the properties of manifolds and smooth
functions in terms of the presence of tangent bundles $TX$ for every
object $X$, forward derivatives and additivity of tangents. They
generalise Cartesian Differential Categories \cite{cdcs}, which are an
axiomatisation of Euclidean spaces and smooth functions.

>>>>

We end this section with a conjecture. Although we have argued above
that there is an analogy between stable functions and smooth
functions, we have not stated any mathematical theorems substantiating
this. \emph{Tangent Categories} \cite{rosický84,cockett14,cockett18} are a
categorical axiomatisation of the properties of manifolds and smooth
functions in terms of the presence of tangent bundles $TX$ for every
object $X$, forward derivatives and additivity of tangents. They
generalise Cartesian Differential Categories \cite{cdcs}, which are an
axiomatisation of Euclidean spaces and smooth functions.
